Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
small updates of abstract

\begin{abstract}
Packet losses are known to affect the performance of latency sensitive applications in the Internet such as media streaming and gaming. 
Transport protocols recover from packet loss in order to provide reliable end-to-end communication and improve user experience. The efficiency of 
loss recovery mechanisms influences the completion time of flows, and thus also the application performance as perceived by the
end user. In this paper we focus on state-of-the-art loss recovery mechanisms for TCP 
and Multipath TCP. We use controlled tail loss scenarios to evaluate the performance of loss recovery mechanisms, and based on the observations, 
we propose an enhanced tail loss recovery mechanism for Multipath TCP, to improve the loss recovery time. Our experiment results using the Linux 
Multipath TCP implementation show consistent end-to-end latency performance improvement in considered scenarios. 
\end{abstract}

@@

The current implementation of TLP is at the TCP flow level. In the event of RTO timeout, the MPTCP retransmission happens with a re-injection in 
to the scheduler along with sending the lost packet on the same path. But in the event of Probe timeout, the loss probe packet is being sent on 
the same path without being re-injected in to the scheduler. We propose a modification to the probe sending mechanism for MPTCP by re-injecting 
the probe packet in to the MPTCP scheduler in the event of PTO. As the probe timeout is meant for acting faster than the RTO timeout with 
essentially the same consequence as a retransmission, it is relevant to follow the same process as upon an RTO. It is expected that this 
modification is useful when the alternate path has lower delay than the packet original transmission path or when there is longer path 
interruption. The timing diagram depicted in Figure~\ref{timingNew} indicates the eventual behavior of modified MPTCP TLP for each of the studied 
loss scenarios. In the case of single packet tail loss, lost packet is retransmitted on the alternate path at the same time as probe sent on primary
path. Since probe is the last transmitted packet, that is same as the retransmitted first outstanding packet in single packet tail loss. When two tail packets are lost,
probe sent on the primary is the last transmitted packet and first outstanding packet is retransmitted on the alternate path. This difference in packet
sequence numbers is expected on the two paths due to the nature of recovery mechanism used in each path. In the case of packet and probe loss in the 
primary path, the alternate path retransmission is same as the probe packet.

>>>>

\begin{abstract}
Packet losses are known to affect the performance of latency sensitive Internet applications such as media streaming and gaming. 
Transport protocols recover from packet loss in order to provide reliable end-to-end communication and improve user experience. The efficiency of 
loss recovery mechanisms influences the completion time of flows, and thus also the application performance as perceived by the
end user. In this paper we focus on state-of-the-art loss recovery mechanisms for TCP 
and Multipath TCP. We use controlled tail loss scenarios to evaluate the performance of loss recovery mechanisms, and based on the observations, 
we propose an enhanced tail loss recovery mechanism for Multipath TCP, to improve the loss recovery time. Our experiment results, using the Linux 
Multipath TCP implementation, show consistent end-to-end latency performance improvement in considered scenarios. 
\end{abstract}

@@

The current implementation of TLP is at the TCP flow level. In the event of RTO timeout, the MPTCP retransmission happens with a re-injection in 
to the scheduler along with sending the lost packet on the same path. But in the event of Probe timeout, the loss probe packet is being sent on 
the same path without being re-injected in to the scheduler. We propose a modification to the probe sending mechanism for MPTCP by re-injecting 
the probe packet in to the MPTCP scheduler in the event of PTO. As the probe timeout is meant for acting faster than the RTO timeout with 
essentially the same consequence as a retransmission, it is relevant to follow the same process as upon an RTO. It is expected that this 
modification is useful when the alternate path has lower delay than the packet original transmission path or when there is longer path 
interruption. The timing diagram depicted in Figure~\ref{timingNew} indicates the eventual behavior of modified MPTCP TLP for each of the studied 
loss scenarios. In the case of single packet tail loss, lost packet is retransmitted on an alternate path at the same time as probe sent on primary
path. Since probe is the last transmitted packet, that is same as the retransmitted first outstanding packet in single packet tail loss. When two tail packets are lost,
probe sent on the primary is the last transmitted packet and first outstanding packet is retransmitted on the alternate path. This difference in packet
sequence numbers is expected on the two paths due to the nature of recovery mechanism used in each path. In the case of packet and probe loss in the 
primary path, the alternate path retransmission is same as the probe packet.
